---  
title: 'Contextual bandit example - data preparation'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(tidyverse)
library(ggthemes)
```


```{r define_functions}
get_summary_results <- function(data){
  data %>% 
    group_by(choice) %>%
	  summarise(n = n(),
		sum_reward = sum(reward),
		mean_reward = mean(reward),
		error_min = qbeta(0.025, 1 + sum_reward, 1 + n - sum_reward),
		error_max = qbeta(0.975, 1 + sum_reward, 1 + n - sum_reward),
		.groups = 'drop') %>% 
    mutate(choice = choice %>% as.factor())
}


plot_summary_results <- function(data){
  data %>% 
    ggplot(aes(x = choice, y = mean_reward)) +
    geom_point() +
    geom_errorbar(aes(ymin = error_min, ymax = error_max), width = 0.1) +
    theme_fivethirtyeight() + 
    theme(axis.title = element_text()) +
    scale_x_discrete(name = 'Choice') +
    scale_y_continuous(name = 'Success rate', labels = scales::percent)
}


get_summary_table <- function(data){
  data %>% 
    summarise(n = n(), .groups = 'drop') %>% 
    mutate(prop = n / sum(n)) %>% 
    kable(format = 'markdown', digits = 3)
}
```

## Introduction
Here, we will use doubly robust offline evaluation to compare various bandit policies (A/B testing, MAB, CB). The dataset used here is from the ["Machine Learning for Personalization" course](http://www.cs.columbia.edu/~jebara/6998/)

## Raw data
The raw data contains 10k rows with a choice (from 10 options), a binary reward, and 100 context features.

```{r load_data, message=FALSE}
url <- 'http://d1ie9wlkzugsxr.cloudfront.net/data_cmab_basic/dataset.txt'

names <- c('choice', 'reward', str_c('x', seq(1:100)), 'empty_col')

raw_data <- read_delim(url, delim = ' ', col_names = names) %>% select(-empty_col)
```


```{r plot_raw_data}
results1 <- raw_data %>%
	group_by(choice) %>%
  get_summary_results()

results1 %>% plot_summary_results()

raw_data %>% 
  group_by(choice) %>% 
  get_summary_table()
  
raw_data %>% 
  group_by(reward) %>% 
  get_summary_table()
```

## Data for simulation
However, in this example, we will only consider observations involving arms 6-10 (4972 rows), which we rename as arms 1-5.
```{r}
data <- raw_data %>%
  filter(choice %in% seq(6, 10)) %>% 
  mutate(choice = choice - 5) %>% 
  mutate(t = 1:n())

data %>% dim()
```

```{r plot_data}
results <- data %>%
	group_by(choice) %>%
	get_summary_results()

results %>% plot_summary_results()
 
data %>% 
  group_by(choice) %>% 
  get_summary_table()

data %>% 
  group_by(reward) %>% 
  get_summary_table()
```

```{r output_data}
data %>% write_csv('../data.csv')
```
